### 2022-11-28 ms.rmd
Added phylogenetic signal calculation. Need to figure out the incoperation of covariance at animal and units level into this calculation as they seem awfully high phylogenetic H2's

>>>>

# Check phylogeneic signal. Need to think about the covariance here. 
    # CTMax - Yes
      phylo_ctmax <- vcv[,"traitctmax:traitctmax.animal"]
      units_ctmax <- vcv[,"traitctmax:traitctmax.units"]

      h2_ctmax = phylo_ctmax / (phylo_ctmax + units_ctmax)
      posterior.mode(h2_ctmax)
      HPDinterval(h2_ctmax)

    # CFL - Yes
      phylo_cfls <- vcv[,"traitcfts:traitcfts.animal"]
      units_cfls <- vcv[,"traitcfts:traitcfts.units"]

      h2_cfls = phylo_cfls / (phylo_cfls + units_cfls)
      posterior.mode(h2_cfls)
      HPDinterval(h2_cfls)

    # z - Yes
      phylo_z <- vcv[,"traittdt_z:traittdt_z.animal"]
      units_z <- vcv[,"traittdt_z:traittdt_z.units"]

      h2_z = phylo_z / (phylo_z + units_z)
      posterior.mode(h2_z)
      HPDinterval(h2_z)
```
